### 2019-08-16 tikz/config.tex
Add many Tikz figures

@@

\tikzstyle{upperbound}=[line cap=round, postaction={decorate,draw,decoration={border, segment length=0.2cm, amplitude=0.3cm, angle=60}}]
\tikzstyle{lowerbound}=[line cap=round, postaction={decorate,draw,decoration={border, segment length=0.2cm, amplitude=0.3cm, angle=-60}}]

@@

\tikzset{%
  pole/.style{%
    color=red,
    cross out,
    draw,
    inner sep=0pt,
    outer sep=0pt,
    minimum size=#1pt
  },
  pole/.default={4}
}

>>>>

\pgfplotsset{
  every axis plot/.append style={line join=round},
  every axis plot/.append style={line cap=round},
}

@@

\pgfplotsset{upperbound}=[line cap=round, postaction={decorate,draw,decoration={border, segment length=0.2cm, amplitude=0.3cm, angle=60}}]
\pgfplotsset{lowerbound}=[line cap=round, postaction={decorate,draw,decoration={border, segment length=0.2cm, amplitude=0.3cm, angle=-60}}]

@@

\pgfplotsset{%
  pole/.style{%
    color=red,
    cross out,
    draw,
    inner sep=0pt,
    outer sep=0pt,
    minimum size=#1pt
  },
  pole/.default={4}
}
